Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands

### 2024-02-13 paper/paper.qmd
Changes made

`nces_district_directory_2018.dta`
This dataset is available from the National Center of Education Statistics [@citeraw2]. This dataset provides a variety of metrics for each district, including the state they are a part of, and their NCES district ID.

`nces_district_enrollment_2018_2020.csv.zip`
This dataset is available from the National Center of Education Statistics [@citeraw2]. This dataset provides a variety of metrics for each district in 2018, 2019, and 2020, including the state they are a part of, their NCES district ID, and the numer of students enrolled for the races: American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races. The original file was a Stata file, however, to reduce the size, data on 2018 and 2019 was removed since they were not required for our paper. Furthermore, the file was converted to a csv file, before then compressing it into a zip file.

`broadband_data_2020October.csv`
This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" Github Repository [@citeraw3]. The data is for October 2020, and gives the broadband usage for each county in the United States, as well as the state that the county is a part of.

>>>>

`nces_district_directory_2018.dta`

This dataset is available from the National Center of Education Statistics [@citeraw2]. This dataset provides a variety of metrics for each district, including the state they are a part of, and their NCES district ID.

`nces_district_enrollment_2018_2020.csv.zip`

This dataset is available from the National Center of Education Statistics [@citeraw2]. This dataset provides a variety of metrics for each district in 2018, 2019, and 2020, including the state they are a part of, their NCES district ID, and the numer of students enrolled for the races: American Indian or Alaska Native, Asian, Black, Hispanic, Native Hawaiian or other Pacific Islander, or Two or more races. The original file was a Stata file, however, to reduce the size, data on 2018 and 2019 was removed since they were not required for our paper. Furthermore, the file was converted to a csv file, before then compressing it into a zip file.

`broadband_data_2020October.csv`

This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" Github Repository [@kahan2020usbroadband]. The data is for October 2020, and gives the broadband usage for each county in the United States, as well as the state that the county is a part of.
